High-Throughput-derived Biologically-Inspired Features for Unconstrained Face Recognition

### 2011-07-01 ivcj_lfw.tex
Changed title
Missing references, typos
More fixes

%===========================================================

@@

\title{
Beyond Simple Features: A Large-Scale Feature Search Approach to Unconstrained Face Recognition
}

@@

% -----------------------------------------------------------------------------
\section{Acknowledgments}
% -----------------------------------------------------------------------------
The authors would like to thank Hanspeter Pfister, Wen-Mei Hwu, Volodymyr
Kindratenko and Jeremy Enos for making additional GPU clusters available for
this work. This work was funded by the Rowland Institute of Harvard, the NVIDIA
Graduate Fellowship, and the National Science Foundation (IIS 0963668).
Hardware support was generously provided by the NVIDIA Corporation.

>>>>

\hyphenation{Bio-logic-ally-ins-pi-red}
%===========================================================

@@

\title{
High-Throughput-derived Biologically-Inspired Features for Unconstrained Face Recognition
}

@@

% -----------------------------------------------------------------------------
\section{Acknowledgments}
% -----------------------------------------------------------------------------
The authors would like to thank Hanspeter Pfister, Wen-Mei Hwu, Vlad
Kindratenko and Jeremy Enos for making additional GPU clusters available for
this work. This work was funded by the Rowland Institute of Harvard, the NVIDIA
Graduate Fellowship, and the National Science Foundation (IIS 0963668).
Hardware support was generously provided by the NVIDIA Corporation.

### 2011-07-01 results.tex
More fixes

\begin{figure*}[ht]
\centering
\subfigure[\small{within-model-class blends}]{
  \includegraphics[scale=0.6]{figures/within_roc.pdf}
  \label{fig:within_rocs}
}
\subfigure[\small{across-model-class blends}]{
  \includegraphics[scale=0.6]{figures/mega_blend_roc.pdf}
  \label{fig:megablend_rocs}
}
\subfigure[\small{comparison with literature}]{
    \small{
    \begin{tabular}{|c||c|c|c|c|}
\hline
%Reference & Kumar et al. ICCV09 \cite{kumar:iccv09} & Wolf et al. ACCV09 \cite{wolf:accv09} & Cao et al. CVPR10 \cite{cao2010face} & This paper \\
 & Kumar et al. & Wolf et al. & Cao et al. & \\
Reference & ICCV09 \cite{kumar:iccv09} & ACCV09 \cite{wolf:accv09} & CVPR10 \cite{cao2010face} & This paper\\
\hline\hline
Mean classification error & 14.7\%$\pm$1.2 & 13.2\%$\pm$0.3 & 15.5\%$\pm$0.5 & \bf{11.9\%$\pm$0.6} \\
\hline
\end{tabular}
    }
\label{fig:table_soa}
}
\caption[]{{\bf ROC curves for various model sub-families on \emph{LFW}
    Restricted View 2.} Curves for \cite{wolf:accv09}, \cite{kumar:iccv09} and \cite{cao2010face}
  are plotted in \ref{fig:megablend_rocs} for reference.  Plots are zoomed-in to
  facilitate comparison.}
\label{fig:roc_curves}
\end{figure*}

\begin{figure*}[ht]
  \centering \subfigure[Misses]{
    \includegraphics[scale=0.8]{figures/misses.pdf}
    \label{fig:misses}
  } \subfigure[False Positives]{
    \includegraphics[scale=0.8]{figures/false_positives.pdf}
    \label{fig:false_positives}
  }
  \caption[]{{\bf Examples of common errors across models.} Misses tend to be
    dominated by differences in view, while false positives frequently occur when
    different individuals share a common view or expression. }
  \label{fig:error_examples}
\end{figure*}

@@

To explore the role of background variation, we evaluated model performance with four different background conditions: no background, white-noise background, phase-scrambled natural backgrounds (i.e. approx. 1/f noise), and natural backgrounds.  Performance as a function of background and variation level is shown Figure \ref{fig:perf_bg_variation}.  Choice of background was found to have a profound effect on model performance.  In the absence of a background, the performance for most models remained high, even at relatively high levels of variation in view, position, and scale (e.g. greater than 90\% performance at variation level 4 for the HT-L3-1st and V1-like models).  However, the inclusion of any background resulted in a precipitous drop-off in performance for all models, except for the HT-L3-1st model, whose performance degraded gradually.  In general, progressively more realistic backgrounds proved increasingly difficult for all models.

>>>>

\begin{figure*}[ht]
\centering
\subfigure[\small{within-model-class blends}]{
  \includegraphics[scale=0.6]{figures/within_roc.pdf}
  \label{fig:within_rocs}
}
\subfigure[\small{across-model-class blends}]{
  \includegraphics[scale=0.6]{figures/mega_blend_roc.pdf}
  \label{fig:megablend_rocs}
}
\subfigure[\small{comparison with literature}]{
    \small{
    \begin{tabular}{|c||c|c|c|c|}
\hline
%Reference & Kumar et al. ICCV09 \cite{kumar:iccv09} & Wolf et al. ACCV09 \cite{wolf:accv09} & Cao et al. CVPR10 \cite{cao2010face} & This paper \\
 & Kumar et al. & Wolf et al. & Cao et al. & \\
Reference & ICCV09 & ACCV09 & CVPR10 & This paper\\
& \cite{kumar:iccv09} & \cite{wolf:accv09} & \cite{cao2010face} & \\
\hline\hline
Average error & 14.7\% & 13.2\% & 15.5\% & \bf{11.9\%} \\
& $\pm$1.2 & $\pm$0.3 & $\pm$0.5 & \bf{$\pm$0.6} \\
\hline
\end{tabular}
    }
\label{fig:table_soa}
}
\caption[]{{\bf ROC curves for various model sub-families on \emph{LFW}
    Restricted View 2.} Curves for \cite{wolf:accv09}, \cite{kumar:iccv09} and \cite{cao2010face}
  are plotted in \ref{fig:megablend_rocs} for reference.  Plots are zoomed-in to
  facilitate comparison.}
\label{fig:roc_curves}
\end{figure*}

\begin{figure*}[ht]
  \centering \subfigure[Misses]{
    \includegraphics[scale=1]{figures/misses.pdf}
    \label{fig:misses}
  } \subfigure[False Positives]{
    \includegraphics[scale=1]{figures/false_positives.pdf}
    \label{fig:false_positives}
  }
  \caption[]{{\bf Examples of common errors across models.} Misses tend to be
    dominated by differences in view, while false positives frequently occur when
    different individuals share a common view or expression. }
  \label{fig:error_examples}
\end{figure*}

@@

To explore the role of background variation, we evaluated model performance with four different background conditions: no background, white-noise background, phase-scrambled natural backgrounds (i.e. approx. 1/f noise), and natural backgrounds.  Performance as a function of background and variation level is shown in Figure \ref{fig:perf_bg_variation}.  Choice of background was found to have a profound effect on model performance.  In the absence of a background, the performance for most models remained high, even at relatively high levels of variation in view, position, and scale (e.g. greater than 90\% performance at variation level 4 for the HT-L3-1st and V1-like models).  However, the inclusion of any background resulted in a precipitous drop-off in performance for all models, except for the HT-L3-1st model, whose performance degraded gradually.  In general, progressively more realistic backgrounds proved increasingly difficult for all models.
